---
title: "AlcoholConsumption"
author: "Team 6_Pentagon"
date: "2023-04-04"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Data Background
The data were obtained in a survey of students math and portuguese language courses in secondary school. It also contains social, gender and study information about students.
## Business Question
How can Universities define counselor hiring needs by predicting students alcohol consumption based on their grade performance and other social factors?

Find people who might be alcoholics? (False positives)/Risk of alcoholism

## Data Cleaning

```{r, cache=TRUE}
student <- read.csv("student-mat.csv", stringsAsFactors = TRUE)
student$totalc <- student$Dalc+student$Walc
student$totalc <- ifelse(student$totalc>2,1,0)
student$Dalc <- NULL
student$Walc <- NULL
str(student)
summary(student)
studentd <- as.data.frame(model.matrix(~.-1, student))

```


## Normalize data
```{r, cache=TRUE}
normalize <- function(x){
  return((x-min(x))/(max(x)-min(x)))
  
}
student_norm <- as.data.frame(lapply(studentd, normalize))

str(student_norm)
summary(student_norm)
```

# Split data
```{r, cache=TRUE}
set.seed(12345)
test_rows <- sample(1:nrow(student_norm), 0.5*nrow(student_norm))
studentdt_test <- studentd[test_rows,]
studentdt_train <- studentd[-test_rows,]
student_test <- student_norm[test_rows, ]
student_train <- student_norm[-test_rows, ]
```

## Regression Model

```{r}
firstmodel <- glm(totalc ~., data= student_train, family = "binomial")
summary(firstmodel)
```

# Predict and Evaluate

```{r}
library(caret)
studentpred <- predict(firstmodel, student_test, type = "response")
modelsuccess <- ifelse(studentpred>=0.4, 1,0)
confusionMatrix(as.factor(modelsuccess), as.factor(student_test$totalc), positive = "1")

```

## KNN Model data cleaning

```{r}
studentk_test <- student_norm[test_rows,-match("totalc",names(student_norm))]
studentk_train <- student_norm[-test_rows,-match("totalc",names(student_norm))]
studentk_test_labels <- student_norm[test_rows,"totalc"]
studentk_train_labels <- student_norm[-test_rows,"totalc"]
```
## Build and Evaluate KNN Model
```{r,cache=TRUE}
library(class)
knn_model <- knn(studentk_train,studentk_test,studentk_train_labels,k=15,prob= TRUE)

library(caret)
confusionMatrix(as.factor(knn_model), as.factor(studentk_test_labels),positive = "1")

```
# Build ANN Model

```{r}

library(neuralnet)
ann_1 <- neuralnet(totalc ~.,data=student_train,hidden=7,2, lifesign ="full")
plot(ann_1)
saveRDS(ann_1,file = 'ann1model.rds')
#Predict Model ANN
ann_1predict <- predict(ann_1,student_test)
ann_1bin <- ifelse(ann_1predict >= 0.25,1,0)
#Evaluate Model ANN
library(caret)
confusionMatrix(as.factor(ann_1bin), as.factor(student_test$totalc), positive = "1")

```
# Decision tree
```{r,cache = TRUE}
#Build Model DT
library(C50)
studenttree <- C5.0(as.factor(totalc) ~., data = studentdt_train)
plot(studenttree)

summary(studenttree)

#Evaluate and predict model
studenttreepred <- predict(studenttree, studentdt_test)
library(caret)
confusionMatrix(as.factor(studenttreepred), as.factor(studentdt_test$totalc), positive = "1")
```

## Random forest
```{r,cache=TRUE}
#Predict RF Model
library(randomForest)
student_rf <- randomForest(as.factor(totalc) ~.,data=student_train)
summary(student_rf)
randomForest::varImpPlot(student_rf)


#Evaluate and Predict RF Model

studentrfpredict <- predict(student_rf, student_test)
summary(studentrfpredict)
confusionMatrix(as.factor(studentrfpredict), as.factor(student_test$totalc), positive = "1")
```
## Stacked Model
## Combine five predicition vectors

```{r,cache=TRUE}

stacked_tele <- data.frame(log_pred = studentpred, KNN = knn_model, ANN = ann_1predict, DT_pred = studenttreepred, rf_pred = studentrfpredict,y = student_test$totalc)

summary(stacked_tele)
```

## Test and Train

```{r}
set.seed(1234)
test_set1 <- sample(1:nrow(stacked_tele), 0.3*nrow(stacked_tele)) 
students_train <- stacked_tele[-test_set1, ]
students_test <- stacked_tele[test_set1, ]

```
## Build Model Stacked Decision tree
```{r}
library(C50)
stackedtree <- C5.0(as.factor(y) ~., data = students_train)
plot(stackedtree)
```

## Predict and Evaluate model
```{r,cache=TRUE}
library(caret)
stackedpredict <- predict(stackedtree,students_test)
confusionMatrix(as.factor(stackedpredict), as.factor(students_test$y), positive = "1")

```

## Cost Consideration
```{r,cache = TRUE}
error_cost = matrix(c(0,1,4,0), nrow =2) 
error_cost

errormodel <- C5.0(as.factor(totalc)~., data = student_train,costs = error_cost)
prederror <- predict(errormodel, student_test)
summary(prederror)
confusionMatrix(as.factor(prederror), as.factor(student_test$totalc), positive = "1")

```

